\begin{abstract}
    The Domain Name System (DNS) is used every day by end users to resolve
    domain names to IP addresses. While the encryption of these queries to hide
    browsing habits from third parties is gaining adoption, it still fails to
    address the privacy issue of sending your identity and destination to a
    single DNS resolver operator. Solutions to this problem by anonymizing the
    client have been proposed, but they fall short in dimensions such as
    performance, threat model, and deployability. While latency is important,
    the other dimensions should also be considered when comparing approaches.
    In this study, we reevaluate DNS-over-HTTPS-over-Tor (DoHoT) and compare it
    against other proposed solutions, taking into consideration additional
    aspects such as threat model and deployability. Additionally, we explore
    various circuit configurations through the Tor network to improve query
    latency when utilizing Tor-based anonymization approaches. We managed to
    decrease the latency of DNS queries while preserving the privacy guarantees
    in our threat model for anonymous resolution. We compare the
    best-performing configuration of Tor-based schemes against other
    approaches. Although the reduced latency is behind that of the other
    solutions, Tor-based approaches are ready for use today with no additional
    infrastructure required, alongside a strong threat model.

    \keywords{DNS \and Oblivious DNS \and Tor \and Encryption \and Proxy \and Latency}
\end{abstract}
