\section{Background and Related Work} \label{sec:background}
The \acf{dns} is a hierarchical and distributed database that maps domain names
to resource records such as IP addresses~\cite{RFC1034,RFC1035}. It enables
human-readable identifiers such as \texttt{example.com} to be translated into
machine-usable network addresses for communication on the Internet.

When a client needs to resolve a domain name, it issues a DNS query, typically
to a \ac{dns} resolver operated by an \ac{isp} or a public \ac{dns} provider.
The resolver acts on behalf of the client to perform a sequence of lookups
through the \ac{dns} hierarchy before responding with the answer back to the
client. Resolvers often cache responses to improve performance and reduce load
on upstream servers. 

\subsection{Encrypted DNS Transport} \label{sec:bg:encr}
Several encrypted transport protocols have been standardized to mitigate the
privacy risks associated with plaintext \ac{dns} queries. These protocols aim
to protect the confidentiality and integrity of \ac{dns} traffic between the
client and the resolver. \acf{dot}~\cite{RFC7858} encapsulates \ac{dns} queries
within a \ac{tls} session, ensuring that on-path observers cannot inspect or
tamper with \ac{dns} traffic. Similarly, \acf{doh}~\cite{RFC8484} transmits
\ac{dns} messages over HTTPS, allowing \ac{dns} queries to blend in with
regular encrypted web traffic. More recently, \acf{doq}~\cite{RFC9250} has been
proposed to reduce latency and connection overhead by using the QUIC transport
protocol, which integrates \ac{tls} over UDP and offers faster handshakes.

While these protocols protect \ac{dns} queries from third-party passive
eavesdroppers on the network path, they do not address a key structural
vulnerability: the resolver remains fully capable of observing and logging all
\ac{dns} queries and client source IP. This exposes users to potential privacy
risks, including profiling, surveillance, or data misuse by the resolver
operator.

\subsection{Tor} \label{sec:bg:tor}
One way to anonymize clients is to leverage an anonymity network. Tor is a
\emph{relative} low-latency anonymity network that protects users against
surveillance and traffic analysis~\cite{dingledine2004}. It achieves anonymity
by routing traffic through a series of volunteer-operated relays and applying
layered encryption such that no single relay knows both the communication's
origin and destination. A typical Tor circuit consists of three relays: an
entry relay, a middle relay, and an exit relay. The entry relay is the only
node that can observe the client's IP address. The middle relay forwards
encrypted traffic between the entry and exit, while the exit relay communicates
with the final destination but does not know the client's IP address.

\subsection{Anonymous Queries} \label{sec:bg:anon}
While encrypted \ac{dns} protocols such as \ac{doh} and \ac{dot} protect query
contents from on-path observers, they do not prevent the resolver from linking
\ac{dns} queries to client identities. Several schemes have been developed
to introduce anonymity into \ac{dns} resolution by explicitly separating the
client from the query.

\subsubsection{Oblivious schemes:}
\ac{odns} uses its own authoritative namespace where the authoritative name
servers act as recursive resolvers~\cite{ODNS}. A client encrypts the domain
name with a key and appends the special-use \ac{tld} \texttt{odns}. The key
itself encrypted using the server's public key. The query and encrypted key are
sent to any resolver, which acts as a proxy and forwards it to the \ac{odns}
server. The server decrypts the key, decrypts the domain, performs
recursion, and returns an encrypted answer via the resolver. The proxy resolver
only sees ciphertext, while the \ac{odns} server cannot identify the client.
Two limitations exist: (i) \ac{ecs}~\cite{RFC7871} in \ac{edns}~\cite{RFC6891}
may de-anonymize clients and should be disabled; (ii) collusion between the
resolver and \ac{odns} server could reveal both identity and query.

\ac{odoh} builds on the idea from \ac{odns} but is instead using the \ac{doh}
transport~\cite{RFC9230}. Clients send encrypted queries to a \ac{doh}
forwarder (the proxy), which relays them to a \ac{doh} server (the target
resolver). The proxy can observe the client's IP address but not the query,
while the target resolver can observe the query but not the client's identity.
This design assumes that the proxy and resolver do not collude, an assumption
that is difficult to verify in practice. The Mutualized Oblivious
DNS ($\mu$ODNS)~\cite{kurihara2023muodns} is an attempt to minimize the
collusion between the relay and the target resolver and corruption of the
client's privacy. For this purpose, multiple relays are selected randomly to be
used towards the target resolver. However, to be the best of our knowledge,
there is a significant lack of global $\mu$ODNS adoption.

The effectiveness of oblivious schemes hinges on the availability of
resolvers and proxies that support the protocols. If this number is limited, it
can hinder the scalability and accessibility of the protocols for end-users.
\ac{odns} needs custom authoritative name servers which also act as recursive
resolvers, and \ac{odoh} needs custom proxies between clients and the recursive
\ac{doh} resolvers. The \ac{odoh} has seen deployment from Cloudflare with
several proxy partners~\cite{singanamalla2020,cfblog}. Cloudflare has also
commented on Mozilla's implementation of \ac{doh} where they suggested that
Firefox also could help with discovering \ac{odoh} proxies which is important
for a widespread adoption of the protocol~\cite{cfmozilla}. 

\subsubsection{Tor-based schemes:}
When a circuit is established in the Tor network to visit a website, the domain
must be resolved at the exit relay. We call this approach \ac{dotor}. Resolving
the domain outside the circuit would expose the destination being accessed. The
specific resolver used for this lookup depends on the exit relay's
configuration, which may point to a local resolver, an \ac{isp} resolver, or a
public resolver.

\ac{dohot} is an alternative method for anonymizing queries introduced by Alec
Muffet~\cite{DoHoT}. By routing \ac{doh} traffic through the Tor network, this
approach enables clients to conceal their identity using Tor's existing relay
infrastructure without requiring additional cryptographic protocols or
specialized infrastructure. The \ac{dns} queries remain encrypted end-to-end
via \ac{doh} and Tor ensures anonymity between the client and the resolver at
the cost of latency. Muffett's extensive home testing during the pandemic
lockdown demonstrated that, despite increased latency, the system maintained
acceptable performance for everyday Internet activities.

\subsubsection{Non-proxy schemes:}
\acf{pir} resolvers aim to circumvent the non-collusion assumptions when
dealing with proxies by having resolvers operating ``in the blind''. This means
resolving domains without knowing what they are using homomorphic encryption
schemes~\cite{xiao2025}. Clients send encrypted queries to a resolver that
cannot learn the requested domain, while cache misses trigger iterative lookups
performed by the client. Authoritative servers privately populate the
resolver's cache using a new EDNS-PR extension proposed by the authors. This
design distributes information exposure across multiple authoritative name
servers, rather than concentrating it at resolvers, thereby raising the bar for
large-scale profiling or collusion at the cost of protocol changes.
