\section{Conclusion} \label{sec:conclusion}

In this study, we explored using the Tor network to anonymize \ac{dns} queries
through the \ac{dohot} approach. Our measurements show that \ac{dohot}
performance can be significantly improved by reducing circuit length to two
hops and by constraining relay selection to localized geographic regions. These
optimizations balance preserving query anonymity in our threat model and
achieving acceptable query latency, making \ac{dohot} a viable option for
privacy-conscious users.

Our findings indicate that the middle relay in Tor's conventional three-hop
design may not be necessary for anonymous \ac{dns} resolution within the bounds
of a non-colluding adversary model. However, omitting it reduces the diversity
of the path and may weaken anonymity in settings with more powerful or
coordinated adversaries.

Localizing the entry and exit relays to the same geographic region as the
client significantly reduced \ac{dns} query latency. However, narrowing the
relay selection pool may reduce entropy in path selection, potentially
increasing the risk of relay-based correlation attacks. This strategy should be
applied with caution depending on the user's threat model and required
anonymity level.

Compared to existing privacy-preserving \ac{dns} protocols like \ac{odns} and
\ac{odoh}, \ac{dohot} benefits from using a well-established anonymity network
without requiring new infrastructure or trust assumptions. However, it inherits
limitations from Tor itself, including potential scalability issues and
susceptibility to censorship. Ultimately, our findings highlight the potential
of Tor-based \ac{dns} anonymization with tailored circuit designs to offer a
practical and privacy-respecting solution for everyday users.
