\section{Discussion} \label{sec:disc}
In this section we compare our measurement results with that of previous
studies around anonymous \ac{dns} queries. We also compare the various schemes
in terms of threat model and deployability in addition to performance.

\subsection{Performance Comparison with Related Work}

Schmitt~\emph{et al.}~\cite{ODNS} compared traditional \ac{dns} resolution with
DNS resolution over the Tor network using the Alexa top 10,000 domains. Their
results showed a median resolution time of 31.31 ms for traditional \ac{dns},
compared to 276.76 ms over Tor. It is important to note that their evaluation
used a setup similar to \ac{dotor}, where DNS queries are resolved in plaintext
at the exit relay. In our measurements around \ac{dotor} we saw a median resolution
time of 250 ms, but managed to reduce it to 50 ms by tuning the circuits for latency.

Singanamalla~\emph{et al.}~\cite{singanamalla2020} evaluated the performance of
\ac{odoh} in a deployment setting, comparing it with several other protocols
including standard \ac{doh}, proxied \ac{doh}, various \ac{odoh}
configurations, DNSCrypt, and \ac{dohot}. They reported an average resolution
time of approximately 300 ms for \ac{odoh}, while \ac{dohot} averaged 696.40
ms. In contrast, our experiments showed a substantially lower average for
\ac{dohot} at 134.48 ms. With a two-hop circuit using relays located in the
same country as the client, the average resolution time was further reduced to
61.69 ms.

Kurihara~\emph{et al.}~\cite{kurihara2023muodns} compared their
collusion-resistant approach to anonymous \ac{dns} queries: $\mu$ODNS, against
variations of ADNSCrypt, as well as DNSCrypt over Tor in terms of performance.
For the Tor-based setting they had two circuit configurations alongside a
client in Japan (jp): (i) an entry in Japan with middle and exit relays
selected globally (i.e., \texttt{jp2any2any}), and (ii) an entry in Japan with
middle and exit relays located in East Asia and East South
Asia\footnote{limited to the following country-codes: cn, hk, jp, kr, tw, kh,
tp, id, my, ph, sg, th and vn}. The median query time of the first setting was
1228.8 ms and the second setting was 461.8 ms. While we used \ac{doh} over Tor
instead of DNSCrypt, the results of our equivalent setting (\texttt{se2any2any}
using the torrc: 88 ms and using \texttt{carml+stem} 130 ms) were nowhere
close to the high latency observed in their experiment.

Xiao~\emph{et al.}~\cite{xiao2025} introduced a way to avoid proxies by having
the resolver resolve domains without knowing what they are using homomorphic
encryption. They highlighted different properties (on-path confidentiality,
client anonymity, and collusion resistance) for various approaches to resolving
\ac{dns} queries and compared them in performance. When comparing their
proposed solution (PDNS) against \ac{dohot}, we assume that they do not
configure any specific circuits (\texttt{any2any2any}). They reported a median
query duration of around 450 ms for \ac{dohot} with HTTPS reuse while their own
solution had a median of 208 ms. Our results show a much lower latency for the
default configuration for \ac{dohot}, going as low as 107 ms.

\subsection{Evaluation Dimensions of Anonymous DNS Schemes}
\iffalse
\begin{table}[h]
    \centering
    \caption{Scheme Evaluation Dimensions}
    \label{tab:eval}
    \begin{tabular}{|l||c|c|c|}
        \hline
        & Performance & Threat Model & Deployability \\
        \hline
        \hline
        ODNS        & High & Low & Low \\\hline
        ODoH        & High & Low & Low \\\hline
        DoHoT       & Low & High & High \\\hline
        DoTor       & Low & High & High \\\hline
        $\mu$ODNS   & Medium & High & Low \\\hline
        PIR         & Medium & High & Low  \\\hline
    \end{tabular}
\end{table}
\fi
When it comes to \emph{performance}, the oblivious single-proxy schemes
(\ac{odns} and \ac{odoh}) achieve low latency but at the cost of a weaker threat
model (prone to collusion). In contrast, Tor-based schemes incur latency
overheads due to the additional anonymization layers. However, as this study has
shown, it is possible to tune the circuits when using the Tor network to reduce
latency by half under a stronger threat model. When it comes to $\mu$ODNS and
\ac{pir} resolvers, they strike a balance between performance overhead and
collusion resistance.

Regarding the \emph{threat model}, the Tor-based schemes, $\mu$ODNS, and \ac{pir}
resolvers are more resistant to collusion compared to the oblivious schemes.
Stronger privacy, therefore, comes at some performance penalty.

Finally, looking at the \emph{deployability}, we can see that Tor-based
solutions have the advantage of utilizing already deployed infrastructure by
simply tunneling \ac{dns} queries through the Tor network. In contrast, the
oblivious schemes and $\mu$ODNS require deployment of new specialized
infrastructure in the \ac{dns} ecosystem. It could also be changes to protocols,
as is the case with \ac{pir} resolvers.

Regardless of performance tradeoffs, practical deployment remains a bottleneck
for many proposed anonymity schemes in \ac{dns}. The choice of scheme is
dependent on the characteristics of the intended use case.


\iffalse
The \ac{dotor} approach sacrifices control for simplicity and (expected) minor
performance gains. Allowing the exit-node to perform the DNS-resolution removes
all control thereof. Anonymity is instead preserved solely by the Tor-circuit.
The main drawbacks here are that the query itself might still be logged even
though it is anonymized. Likewise, should an adversary control either node in a
circuit consisting only of a guard and exit (e.g. se2se) in addition to the
network it could theoretically be possible to correlate the query and the
client.
\fi

\subsection{Limitations}
Our experiments primarily measured \ac{dns} query latency using NXDOMAIN
lookups. This approach eliminates caching as a variable and does not accurately
reflect real-world usage, where cache hits are common. Depending on the
measurement targets and caching effects of the related works, the NXDOMAIN
queries could also explain some of our lower latency results for comparison.

\iffalse
\begin{table}[h!]
    \centering
    \caption{Comparative Evaluation Dimensions}
    \label{tab:comp}
    \begin{tabular}{|c|c|c|c|}
         \hline
         Approach & Latency & Anonymity & Deployability \\\hline
         \hline
         Do\{T,H,Q\} & Low      & None      & High   \\\hline
         ODNS        & Medium   & Medium    & Low    \\\hline
         ODoH        & Low      & Medium    & Medium \\\hline
         DoHoT 1.0   & High     & High      & High   \\\hline
         DoHoT 2.0   & Medium   & High      & High   \\\hline
    \end{tabular}
\end{table}
\fi


