\section{Introduction} \label{sec:intro}

The \ac{dns} is a foundational Internet protocol for translating human-readable
domain names into resources, such as IP addresses~\cite{RFC1034,RFC1035}.
Whenever a user accesses a website or online service, a \ac{dns} query is
issued, and these queries have historically been sent in plaintext, exposing
users to surveillance, censorship, and profiling by network
adversaries~\cite{HoangNDKLMCGP21,KimZ15,PearceJLEFWP17}.

To address these concerns, privacy-enhancing protocols
\cite{RFC8484,RFC7858,RFC9250} have been standardized and deployed that encrypt
the communication between the client and the resolver, preventing on-path
network adversaries from inspecting or modifying the query contents. However,
these protocols do not anonymize the client: the resolver still sees both the IP
address of the client \emph{and} the contents of the query. This data is highly
sensitive as it can reveal interests, routines, and affiliations of individuals,
as well as operational details of organizations \cite{resolver-wiretap,RFC9076}.
Importantly, these risks affect not only end users, whose activities may be
exposed, but also resolver operators, who must safeguard their privileged
systems, and the data they process and collect. Even in jurisdictions with
strong privacy laws preventing the monetization of this type of data, there are
data breaches and leakage risks.

To break this direct link between client identity and \ac{dns} query content,
new protocols have been proposed. \emph{Oblivious} protocols introduce a
dedicated relay (or proxy) between the client and the resolver so that no single
entity can observe both ends of the query~\cite{RFC9230,ODNS}. \emph{Tor-based}
solutions use the Tor network~\cite{dingledine2004} to separate the client
identity from the query~\cite{DoHoT}. Another recent proposal involves
integrating \ac{pir} to \ac{dns} resolvers leveraging homomorphic encryption
schemes~\cite{xiao2025}. The client sends an encrypted query, the resolver
computes over encrypted data using homomorphic encryption, and returns an
encrypted response that the client decrypts locally, ensuring the resolver never
learns the requested domain. Comparing these proposals solely in terms of query
latency, which is a pain point for both encrypted and anonymous \ac{dns}
transport, places the Tor-based solutions dead
last~\cite{RFC9230,kurihara2023muodns,ODNS,xiao2025}.

In this paper, we compare different anonymous query schemes in terms of query
latency, \emph{threat model}, and deployability concerns. We explore how Tor's
latency overhead can be reduced \emph{while at the same time} still provide
stronger privacy guarantees for \ac{dns} resolution compared to related work. We
are not trying to hide that the client is communicating with a \ac{dns}
resolver. The query content must be hidden from the relays while keeping the
client source IP hidden from the \ac{dns} resolver. That is why this study
investigates the viability of using two-hop Tor circuits and restricting relays
to geographic regions in close proximity to the client. Our main contributions
are as follows:

\begin{itemize}
    \item An analysis of threat models, showing that two-hop circuits and
        geographically close relays in Tor still provide stronger
        privacy-protections than oblivious single-proxy schemes. Default Tor
        defends against path adversaries, while anonymous DNS has the resolver
        as the adversary. Privacy means hiding the client source IP from the
        resolver, not the fact it contacted a resolver.
    \item By using two-hop circuits and placing relays in relative close
        proximity to the client, it is possible to cut the average query
        latency of Tor-based solutions such as DoHoT in half (from
        134$\pm$110ms to 61$\pm$135ms) 
    %\item We compare different anonymous query schemes in terms of query
        %latency, threat model, and deployability, emphasizing that more than
        %query latency should be taken into consideration when selecting a scheme
        %for anonymizing \ac{dns} queries.
\end{itemize}

Section~\ref{sec:background} presents background and related work. We define
threat models for DNS queries in the context of Tor in
Section~\ref{sec:threatmodel}. Section~\ref{sec:method} covers our network
measurements methodology, followed by measurement results in
Section~\ref{sec:measurement}. We discuss and ground our results in related work
in Section~\ref{sec:disc}. Section~\ref{sec:conclusion} concludes the paper.