\section{Method} \label{sec:method}

Our threat model considers a passive adversary with visibility over a
\emph{single} segment of the \ac{dohot} communication path. The adversary may
monitor one of the following: (1) The client's connection to the Tor network
(entry relay). (2) The encrypted traffic between Tor relays. (3) The encrypted
traffic between the exit relay and \ac{doh} resolver. (4) The \ac{doh} resolver
itself.

At the Tor entry relay, the adversary can see the client's IP address and
encrypted Tor traffic but cannot see \ac{dns} queries or \ac{doh} endpoints. At
the Tor exit relay or on the path to the \ac{doh} server, the adversary can
view encrypted \ac{doh} traffic but cannot link it to the client's IP address.
At the \ac{doh} resolver, the adversary sees decrypted \ac{dns} queries and the
Tor exit IP but not the client IP. Our model reflects practical threats such as
surveillance by \acp{isp} (at the Tor entry), data collection by \ac{doh}
resolvers, and network-level observation (e.g., nation-state monitoring of exit
traffic), while emphasizing query confidentiality and client anonymity within
the constraints of Tor's threat model and the encryption guarantees by
\ac{doh}.

For \ac{dohot} we use the implementation proposed by Alec Muffet as a
foundation. We dockerize both Tor and DNSCrypt-proxy to a single container to
simplify the deployment and measurement. DNSCrypt-proxy is responsible for
listening on a port for client queries and sending them to a \ac{doh} server
using Tor. We decided to pick a single \ac{doh} provider for our measurements
to limit the number of variables. Our choice of \ac{doh} resolver, 
Cloudflare's \texttt{1.1.1.1}, is
using anycast which means that the closest from the perspective of our exit or
proxy will be used\footnote{\url{https://developers.cloudflare.com/1.1.1.1/}}.

On the container we install two additional tools for interacting with
the Tor client. \texttt{Carml} is a command-line tool and Python library that
lets users interact with a running Tor instance~\cite{carml}. It offers simple
commands to view and create circuits, manage streams, and set up hidden
services. \texttt{Stem} is a Python library from the Tor Project used to
control and script Tor through its Control Protocol~\cite{stem}. It lets
developers build custom tools to fetch available relays and manage Tor
processes programmatically. 

As mentioned in Section~\ref{sec:intro}, we focus on two approaches for
reducing latency in Tor circuits: \emph{number} of relays and \emph{location}
of relays. The configuration file for Tor, the \texttt{torrc}, does not allow
anything less than three relays for a circuit, but we can specify the
geographical location of the entry and the exit using country-codes. Since the
client for our measurements is located in Sweden (country-code: \texttt{se}), choosing Tor
relays in Sweden places them in close geographic proximity to the client. Using
\texttt{carml} and \texttt{stem} we are able to both specify the geographical
location of the middle relay in a three-hop circuit, as well as build two-hop
circuits without a middle relay.

\iffalse
\begin{table}[h!]
    \centering
    \caption{Table of measurement configurations using Tor.}
    \label{tab:conf}
    \begin{tabular}{|c|c|c|c|c|c|c|}
         \hline
         ID & protocol & method & hops & entry & middle & exit \\\hline
         \hline
         1 & dohot & torrc & 3 & random & random & random \\\hline
         2 & dohot & torrc & 3 & sweden & random & random \\\hline
         3 & dohot & torrc & 3 & sweden & random & sweden \\\hline
         4 & dohot & carml+stem & 3 & random & random & random \\\hline
         5 & dohot & carml+stem & 3 & sweden & random & random \\\hline
         6 & dohot & carml+stem & 3 & sweden & random & sweden \\\hline
         \hline
         7 & dohot & carml+stem & 3 & random & sweden & random \\\hline
         8 & dohot & carml+stem & 3 & sweden & sweden & random \\\hline
         9 & dohot & carml+stem & 3 & random & sweden & sweden \\\hline
         10 & dohot & carml+stem & 3 & sweden & sweden & sweden \\\hline 
         \hline
         11 & dohot & carml+stem & 2 & random & - & random \\\hline
         12 & dohot & carml+stem & 2 & sweden & - & random \\\hline
         13 & dohot & carml+stem & 2 & random & - & sweden \\\hline
         14 & dohot & carml+stem & 2 & sweden & - & sweden \\\hline
    \end{tabular}
\end{table}

Rows 1--3 in Table~\ref{tab:conf} present configuration variations using the
Tor configuration file (\texttt{torrc}). In this setup, it is not possible to
reduce the number of hops below three, nor to specify the geographical location
of the middle relay.

Rows 4--6 show equivalent configurations constructed with \texttt{carml} and
\texttt{stem}, enabling a comparison between Tor's default relay selection
algorithm and the custom approach.

Rows 7--10 demonstrate configurations where the middle relay is explicitly
specified in a three-hop circuit using \texttt{carml} and \texttt{stem}, a
capability not available through \texttt{torrc} alone.

Finally, rows 11--14 illustrate two-hop circuit configurations, which are only
achievable when using \texttt{carml} and \texttt{stem}.
\fi


For \ac{odoh}, we also rely on DNSCrypt-proxy based container to foward \ac{dns} queries
to \ac{doh} resolvers through \ac{odoh} infrastructure: relay and target. We follow
a similar approach as for \ac{dohot} and configure DNSCrypt-proxy to forward encrypted
client query to Cloudflare \ac{doh} resolvers through an \ac{odoh} relay in
Sweden. This ensure that, the \ac{odoh} relay and the target resolver are not
conflicting. Moreover, by using an \ac{odoh} relay in Sweden, we mimic the \ac{dohot}
case where the Tor entry relay is in Sweden. Furthermore, to be consistent with
\ac{dohot} experiments, we also use Cloudflare \ac{doh} resolver as target. Note that,
$\mu$\ac{odns} is not considered in this study as it not based on the popular
DNSCrypt-proxy and his adoption is considerably limited. Based on this
configuration, we create container and apply exactly the same measurement cases
as for \ac{dohot}. 

\todo{DoTor (Tor Arvill)}

To eliminate the effects of caching and to maintain consistency across tests,
we issue queries for uniquely generated \acp{sld} under a valid \ac{tld}, which
are expected to return an non-existing-domain return code (NXDOMAIN). This
approach ensures that the observed latency mainly reflects the path between the
client and the resolver rather than the influence of cache hits or additional
authoritative name servers. For each configuration we repeat the measurement
1000 times. In each iteration, we start the container with the specified
configuration and wait until a circuit is established and a query receives a
successful response. We then issue a query for an A record using a unique,
non-existent domain and measure the time, in milliseconds, for the reply to
return. Finally, we stop the container before the next iteration
begins. The code for the containers and measurement script can be found on 
GitHub.\footnote{\todo{add github link}}

